resistanceModelNotesAndy

### 2016-02-11 resistanceModelNotesAndy.Rmd
notes

@@

@@

~ add default curtis values to UI labels in server.r
~ check on plotting of combined strategy
~

@@

Tighten up the story before sending to Ian, I'm getting there. Maybe put into a summary Rmd pdf.

## IDEA
# rather than trees of e.g. mix1 better than sequence I could show time-to-resistance mix1-sequence.

OR I could even put time_to_resistance on the same plot for each stratgey (maybe with exposure on the x-axis)
This is very similar to some plots I have already, I just need to remove the facetting by strategy and remove individual strategies.

## BEWARE what am I doing with putting mixture better than seq on each repeated input ....  
## e.g. it doesn't seem to quite make sense that I have mixture or sequence better for insecticide1
## but maybe it is because all the inpiuts are repeated

@@

~ do PRCCs on whether mixture or sequential better

~ tomorrow when on good form in morning work out how best to summarise for Ian

~ add other resist thresholds into PRCC.

@@

# would it be useful for Ian for me to create an interactive shiny app to view the 1000 sim data. E.g. could just have the ggplot code with options to set the x value & colour by different inputs.

# maybe add in a loop to plot for all 3 resistance thresholds
# maybe try faceting by parameter ranges ?
# lookup to see if I can steal any existing sensi analysis type code

See sensiAnPaperPartOneAtATime.r
  #TODO I need to think more carefully about how to do this
  #and look back at my existing notes
1. Graphs where just change one param at a time. Jo Lines/Andy conversation at TAG.

Extended Curtis requests from Ian (still not quite sure how I will do)
1. 'Male exposure' as a proportion of female (0.5 to 1)
Exposure is held in array a, read from input file by sex, line 90.
    a['m','0','0'] <- input[8,i]
I can add a parameter to the setExposure() function which is called from sensiAnPaperPart.r

1. look at investigating response by changing single parameters at a time (or can I use existing runs)
results files are in 'C:\\Users\\andy\\Documents\\resistanceResultsBackup\\listOutI1_1000.rda'
listOut2, & listOutMix

1. create a vignette that shows how best to run current model

1. I could ad something to shinyCurtis with a message at the top saying whether mixture or sequence better and maybe an arrow pointing to it.

1. fix the testthat tests to avoid new input addition

1. create functions fitnessLocus(), fitnessNiche(), fitnessIndiv()

@@

1. submit stackoverflow question about createArray2(), including about n=3 in eval.parent
1. what to call createArray2() ? maybe namedArray, or arrayNamed() ? could even put back in the option to pass the fill value ? submit to stackoverflow ?

1. maybe add option in setInputSensiScenarios to save input object as a csv or rda.

1. add some defensive checks, e.g. for sensible input variables

1. create a vignette from first shiny app documenting how the model works

1. finish tidying documentation of reading in input vars in createInputMatrix()

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario

@@

### refactoring variables to arrays
Refactoring to arrays reduces code volume, reduces risk of mistyped variable names and allow objects to be passed between functions.
cis/trans makes it slightly tricky, but not all variables have cis/trans
only used for genotype frequencies (f) and in output matrices fitness & genotype 
in the wild in Beths code :
```
fs.m.RS1RS2_cis <- f.m.RS1RS2_cis
fs.m.RS1RS2_trans <- f.m.RS1RS2_trans
```

@@

### refactoring, what I have done
Replaced the following collections of individual variables with arrays :
(To reduce code volume, reduce risk of mistyped variable names and allow objects to be passed between functions. Also potentially allows it to cope with more loci and/or niches later).

>>>>

Extended Curtis requests from Ian
1. 'Male exposure' as a proportion of female (0.5 to 1)
Exposure is held in array a, read from input file by sex, line 90.
    a['m','0','0'] <- input[8,i]
I can add a parameter to the setExposure() function which is called from sensiAnPaperPart.r

@@

** 11/2/16 **
~ added default curtis values to UI labels in server.r

@@

~ check on plotting of combined strategy, i think I may not be doing it right

~ for the paper we could have a couple of figures that show how a relatively small change to effectiveness can alter the curtis plot.

effectI2 from 1 to 0.85, & resistance arises faster for mix1 than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.85 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )

effectI2 from 1 to 0.5, & resistance arises faster for mix2 than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 0.5 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43 )

@@

@@

@@

# would it be useful for Ian for me to create an interactive shiny app to view the 1000 sim data. E.g. could just have the ggplot code with options to set the x value & colour by different inputs.
# maybe try faceting by parameter ranges ?

1. create a vignette that shows how best to run current model
1. fix the testthat tests to avoid new input addition
1. create functions fitnessLocus(), fitnessNiche(), fitnessIndiv()

@@

1. submit stackoverflow question about createArray2(), including about n=3 in eval.parent
1. what to call createArray2() ? maybe namedArray, or arrayNamed() ? could even put back in the option to pass the fill value ? submit to stackoverflow 
1. maybe add option in setInputSensiScenarios to save input object as a csv or rda.
1. add some defensive checks, e.g. for sensible input variables

@@

@@
